### 2021-09-27 博士/论文提交/adversarial_attack/TCSVT/大修/response/response.tex

% 消融实验：噪声攻击。
(4) We have added a new experiment to evaluate the attack performance of the random patterns.

% 消融实验
(5) We have added a new experiment to evaluate the attack performance when only adding the perturbation to the search/template image.

% 引用论文
(6) We have added 3 papers published in the IEEE Transactions on Circuits and Systems for Video Technology, which are most closely related to our manuscript, and analysed what is distinctive / new about our current manuscript related to these previously published papers. For your convenience in cross-checking, the new text is given as follows.

\uline{
Some recent research topics which are mostly related to adversarial attack also include digital watermarking [33], 3D face presentation attacks to the face recognition networks [34] and adversarial defense for image classifiers [26].
Xiong \textit{et al.} [33] propose to generate the digital watermarking by slightly modifying the pixel values of video frames to protect video content from unauthorized access. Compared with [33], our purpose of modifying pixel values of video frames is attacking the tracker, instead of detecting the illegal distribution of a digital movie.
Jia \textit{et al.} [34] propose to generate 3D face artifacts to attack the face recognition network. Compared with [34], our method directly modifies the input of the network instead of changing the input of cameras using 3D face artifacts.
Wang \textit{et al.} [26] propose the white-box attack/defense methods for image classifiers. Compared with [26], we focus on attacking the object tracking networks instead of the image classification networks.
}

@@

\textbf{Sorry for the inconvenience of reading Fig. 9 caused by the small font size.
We are willing to adjust Fig. 9 font size to make it easier to read on the computer, but because we have added many ablation experiments to revised manuscript, the total number of pages exceeds the maximum page limit for TCSVT (i.e., 14 pages). Therefore we have to remove the analysis of the attack performance for each attribute of the OTB as well as Fig. 9.
}

%%%% 问题 1.4 %%%%
\textit{Also, some recent papers are valued to be referred (2020-2021), to enhance the quality.}

\textbf{Thanks for the good comments. We have added several 2020-2021 related papers to enhance the quality of the revised manuscript. For your convenience of cross review, the new text is given as follows.}

\uline{Some recent research topics which are mostly related to adversarial attack also include digital watermarking [33], 3D face presentation attacks to the face recognition networks [34] and adversarial defense for image classifiers [26].
Xiong \textit{et al.} [33] propose to generate the digital watermarking by slightly modifying the pixel values of video frames to protect video content from unauthorized access. Compared with [33], our purpose of modifying pixel values of video frames is attacking the tracker, instead of detecting the illegal distribution of a digital movie.
Jia \textit{et al.} [34] propose to generate 3D face artifacts to attack the face recognition network. Compared with [34], our method directly modifies the input of the network instead of changing the input of cameras using 3D face artifacts.
Wang \textit{et al.} [26] propose the white-box attack/defense methods for image classifiers. Compared with [26], we focus on attacking the object tracking networks instead of the image classification networks.
}

@@

\textit{My major concern is that the writing and organization need to be carefully modified and optimized. Besides, 1. Authors are focused on the anchor-free tracker in the experiments, but the anchor-free Siamese trackers are not well mentioned. I suggest the authors to include the discussion of state-of-the-art of other similar approaches (e.g., FCOT, SiamCAR, OCEAN, et. al.).}

\textbf{We have discussed several state-of-the-art anchor free Siamese trackers at the related work. For your convenience of cross review, the new text is given as follows.}

\uline{In this anchor-free paradigm, many recent works (e.g., [20], [21], [22]) are dedicated to more robust and efficient visual tracking based on various anchor-free settings.
% Ocean
Ocean [20] directly predicts the position and scale of target objects in an anchor-free fashion; since each sample position in groundtruth boxes is well trained, the tracker is capable of rectifying inexact predictions of target objects during inference.
% FCOT
FCOT [21] introduces an online regression model generator (RMG) based on the carefully designed anchor-free box regression branch, which enables the tracker to be more effective in handling target deformation during tracking procedure.
%  SiamCAR
SiamCAR [22] is both anchor and proposal free, and takes one unique response map to predict object location and bounding box directly; this setting significantly reduces the number of hyper-parameters, which keeps the tracker from complicated parameter tuning and makes the tracker significantly simpler, especially in training.
}

\textbf{Besides, we have evaluated the transferability to the anchor free tracker OCEAN in Setcion IV.F of the revised manuscript. For your convenience of cross review, the new text is given as follows.}
